The \Prob

### 2013-03-05 bikes/bikes.tex
a little more

\newcommand\BA{\cellcolor{WildStrawberry}~\textcolor{White}{$b_0$}}
\newcommand\BB{\cellcolor{NavyBlue}      ~\textcolor{White}{$b_1$}}
\newcommand\BC{\cellcolor{OliveGreen}   ~\textcolor{White}{$b_2$}}
\begin{figure*}[t]
	\begin{center}
	\begin{subfigure}[b]{0.25\textwidth}
		\begin{tabular}{rp{1.5em}|p{1.5em}|}
		& \multicolumn{2}{c}{distance} \\
		person & \multicolumn{1}{|c|}{0} & \multicolumn{1}{c|}{1} \\
		\hline
		\multicolumn{1}{r|}{\PA} & \BA & \\
		\cline{2-3}
		\multicolumn{1}{r|}{\PB} & & \BA \\
		\cline{2-3}
		\multicolumn{3}{c}{}\\
		\multicolumn{3}{c}{}\\
		\multicolumn{3}{c}{}\\
		\end{tabular}
		\caption{$2$ people, $1$ bike.}
	\end{subfigure}
	\begin{subfigure}[b]{0.3\textwidth}
		\begin{tabular}{rp{1.5em}|p{1.5em}|p{1.5em}|}
		& \multicolumn{3}{c}{distance} \\
		person & \multicolumn{1}{|c|}{0} & \multicolumn{1}{c|}{1} & \multicolumn{1}{c|}{2} \\
		\hline
		\multicolumn{1}{r|}{\PA} & \BA & \BA & \\
		\cline{2-4}
		\multicolumn{1}{r|}{\PB} & & \BB & \BB \\
		\cline{2-4}
		\multicolumn{1}{r|}{\PC} & \BB & & \BA \\
		\cline{2-4}
		\multicolumn{4}{c}{}\\
		\multicolumn{4}{c}{}\\
		\end{tabular}
		\caption{$3$ people, $2$ bikes.}
	\end{subfigure}
	\begin{subfigure}[b]{0.35\textwidth}
		\begin{tabular}{rp{1.5em}|p{1.5em}|p{1.5em}|p{1.5em}|p{1.5em}|}
		& \multicolumn{5}{c}{distance} \\
		person & \multicolumn{1}{|c|}{0} & \multicolumn{1}{c|}{1} & \multicolumn{1}{c|}{2} & \multicolumn{1}{c|}{3} & \multicolumn{1}{c|}{4} \\
		\hline
		\multicolumn{1}{r|}{\PA} &\BA&\BA&\BA&   & \\
		\cline{2-6}
		\multicolumn{1}{r|}{\PB} &   &\BB&\BB&\BB& \\
		\cline{2-6}
		\multicolumn{1}{r|}{\PC} &   &   &\BC&\BC&\BC\\
		\cline{2-6}
		\multicolumn{1}{r|}{\PD} &\BB&   &   &\BA&\BA\\
		\cline{2-6}
		\multicolumn{1}{r|}{\PE} &\BC&\BC&   &   &\BB\\
		\cline{2-6}
		\end{tabular}
		\caption{$5$ people, $3$ bikes.}
	\end{subfigure}
	\end{center}
	\caption{Bicycle allocation policies for selected instances of the \prob. White cells represent walking; cells of different colours represent different bikes.}
	\label{fig:grids}
\end{figure*}

>>>>

\newcommand\BA{\cellcolor{WildStrawberry}~\textcolor{White}{$b_0$}}
\newcommand\BB{\cellcolor{NavyBlue}      ~\textcolor{White}{$b_1$}}
\newcommand\BC{\cellcolor{OliveGreen}   ~\textcolor{White}{$b_2$}}
\begin{figure*}[t]
	\begin{subfigure}[b]{0.28\textwidth}
		\begin{tabular}{rp{1.5em}|p{1.5em}|}
		& \multicolumn{2}{c}{distance} \\
		person & \multicolumn{1}{|c|}{0} & \multicolumn{1}{c|}{1} \\
		\hline
		\multicolumn{1}{r|}{\PA} & \BA & \\
		\cline{2-3}
		\multicolumn{1}{r|}{\PB} & & \BA \\
		\cline{2-3}
		\multicolumn{3}{c}{}\\
		\multicolumn{3}{c}{}\\
		\multicolumn{3}{c}{}\\
		\end{tabular}
		\caption{$2$ people, $1$ bike.}
	\end{subfigure}
	\begin{subfigure}[b]{0.33\textwidth}
		\begin{tabular}{rp{1.5em}|p{1.5em}|p{1.5em}|}
		& \multicolumn{3}{c}{distance} \\
		person & \multicolumn{1}{|c|}{0} & \multicolumn{1}{c|}{1} & \multicolumn{1}{c|}{2} \\
		\hline
		\multicolumn{1}{r|}{\PA} & \BA & \BA & \\
		\cline{2-4}
		\multicolumn{1}{r|}{\PB} & & \BB & \BB \\
		\cline{2-4}
		\multicolumn{1}{r|}{\PC} & \BB & & \BA \\
		\cline{2-4}
		\multicolumn{4}{c}{}\\
		\multicolumn{4}{c}{}\\
		\end{tabular}
		\caption{$3$ people, $2$ bikes.}
	\end{subfigure}
	\begin{subfigure}[b]{0.38\textwidth}
		\begin{tabular}{rp{1.5em}|p{1.5em}|p{1.5em}|p{1.5em}|p{1.5em}|}
		& \multicolumn{5}{c}{distance} \\
		person & \multicolumn{1}{|c|}{0} & \multicolumn{1}{c|}{1} & \multicolumn{1}{c|}{2} & \multicolumn{1}{c|}{3} & \multicolumn{1}{c|}{4} \\
		\hline
		\multicolumn{1}{r|}{\PA} &\BA&\BA&\BA&   & \\
		\cline{2-6}
		\multicolumn{1}{r|}{\PB} &   &\BB&\BB&\BB& \\
		\cline{2-6}
		\multicolumn{1}{r|}{\PC} &   &   &\BC&\BC&\BC\\
		\cline{2-6}
		\multicolumn{1}{r|}{\PD} &\BB&   &   &\BA&\BA\\
		\cline{2-6}
		\multicolumn{1}{r|}{\PE} &\BC&\BC&   &   &\BB\\
		\cline{2-6}
		\end{tabular}
		\caption{$5$ people, $3$ bikes.}
	\end{subfigure}
	\caption{Bicycle allocation policies for selected instances of the \prob. White cells represent walking; cells of different colours represent different bikes.}
	\label{fig:grids}
\end{figure*}

The pattern is now evident: Person $i$ picks up a bike at distance $i$ and drops it off at distance $i+k~\mathsf{mod}~n$.
%TODO
%In the notation from the previous section:
%\begin{eqnarray*}
%	p_i  &=&
%\end{eqnarray*}

We now show that this strategy is both possible and optimal.

\newtheorem{theorem}{Theorem}

\begin{theorem}[Bicycle Allocation]
The \prob~is solved optimally when $p_i$ rides a bike between distance $i$ and distance $i+k~\mathsf{mod}~n$.
\end{theorem}
\begin{proof}
By condition (3) above, it suffices to show that, at each distance unit, exactly $k$ people ride.
% TODO
\end{proof}
